FTLR proof cases

### 2018-07-01 fully-abstract-comp/ftlr-proof-cases.tex
Sealed case.

    \end{itemize}
  \item \label{case:ftlr:move-cca-etc} All of the following hold: (includes cap-manipulation cases: move, cca,
    restrict, seta2b, cseal, split, splice, that can be handled mostly
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq
      \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}}
      \neq \failed$
    \item $r_i \neq \pcreg$ for all $i$
    \item One of the following holds:
      \begin{enumproof}
      \item \label{case:ftlr:move-cca-etc:cca-normal} (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,
        $w_1' = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\Phi_T(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k =
        1$
      \item \label{case:ftlr:move-cca-etc:cca-stack}(restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,
        $w_1' = ((\perm',\linear),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi_T(r_1) =
        ((\perm,\linear),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$,
        $k = 1$
      \item \label{case:ftlr:move-cca-etc:cca-seal}(cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,
        $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $\Phi_S(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k = 1$
      \item \label{case:ftlr:move-cca-etc:move}(move) $w_1 = \Phi_S(r_2)$, $w_1' = \Phi_T(r_2)$, and $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $r_1 \neq r_2$ and $k = 2$.
      \item \label{case:ftlr:move-cca-etc:move-eq}(move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_T(r_1)$ and $k = 1$.
      \item \label{case:ftlr:move-cca-etc:cseal}(cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' =
        \sealed{\sigma,\Phi_T(r_1)}$, $\Phi_S(r_2) = \Phi_T(r_2) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k=1$
      \item \label{case:ftlr:move-cca-etc:split-normal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$, $s < \eaddr$,
        $w_1 = w_1' = ((\perm,\lin),\baddr,n,\aaddr)$, $w_2 = w_2' =
        ((\perm,\lin),n+1,\eaddr,\aaddr)$, $w_3 = w_3' = \linCons{\Phi_S(r_3)}$, $k=3$.
      \item \label{case:ftlr:move-cca-etc:split-seal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \leq s$, $s <
        \sigma_\eaddr$, $w_1 = w_1' = \seal{\sigma_\baddr,s,\sigma}$, $w_2 =
        w_2' = \seal{s+1,\sigma_\eaddr,\sigma}$, $k=2$.
      \item \label{case:ftlr:move-cca-etc:split-stack} (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,
        $\Phi_T(r_3) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$,
        $s < \eaddr$, $w_1 = \stkptr{\perm,\baddr,n,\aaddr}$, $w_1' =
        ((\perm,\linear),\baddr,s,\aaddr)$, $w_2 =
        \stkptr{\perm,s+1,\eaddr,\aaddr}$,

@@

  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump. If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.} and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.} as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\normal),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrvg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  Case \ref{case:ftlr:scall:reg}:

  First, from reasonability of $\Phi_S$, we get that $\Phi.\reg(r)$ is reasonable in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$ up to $n-1$ steps for all $r \neq \pcreg$.
  Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} then tells us that
  $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrr(W_R)$.

  We then need to split the ownership of $W_R'$.
  From assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, and we get from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity} that
  $\npair[n-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrrg{\trust}(\{\rdata,\rstk,\rtmp{1},r_1,r_2,\rretd,\rretc\})(W_R'')$ for the appropriate $W_R''$.

  To obtain $\npair[n-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrr(\{\rdata\})(W_R')$, it remains to prove the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know
    \[
      \npair[n]{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrvg{\trust}(W_{R,\stk})
    \]
    which by the $\mathit{stackReadCondition}$ gives $S \subseteq \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n]{[\baddr_\stk,\eaddr_\stk]} \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

    TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-normal}:
    From $\npair{(\Phi_S(r_3),\Phi_S(r_3))} \in \lrvg{\trust}(R_R(r_3))$, Lemma~\ref{lem:splitting-safety-normal} gives us $W_1$, $W_2$ and $W_3$ such that $R_R(r_3) = W_1 \oplus W_2 \oplus W_3$ and $\npair{(w_1,w_1) \in \lrvg{\trust}(W_1)}$, $\npair{(w_2,w_2) \in \lrvg{\trust}(W_2)}$ and $\npair{(w_3,w_3) \in \lrvg{\trust}(W_3)}$.
    We take $R_R'(r_1) = W_1$, $R_R'(r_2) = W_2$ and $R_R'(r_3) = W_3 \oplus R_R(r_1) \oplus R_R(r_2)$ and $R_R' = R_R(r)$ elsewhere.

>>>>

    \end{itemize}
  \item \label{case:ftlr:move-cca-etc} All of the following hold: (includes cap-manipulation cases: move, cca,
    restrict, seta2b, cseal, split, splice, that can be handled mostly
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq
      \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}}
      \neq \failed$
    \item $r_i \neq \pcreg$ for all $i$
    \item One of the following holds:
      \begin{enumproof}
      \item \label{case:ftlr:move-cca-etc:cca-normal} (restrict,cca,seta2b) $w_1 = ((\perm',\lin),\baddr,\eaddr,\aaddr')$,
        $w_1' = ((\perm',\lin),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\Phi_T(r_1) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$, $k =
        1$
      \item \label{case:ftlr:move-cca-etc:cca-stack}(restrict,cca,seta2b) $w_1 = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$,
        $w_1' = ((\perm',\linear),\baddr,\eaddr,\aaddr')$, $\Phi_S(r_1) =
        \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi_T(r_1) =
        ((\perm,\linear),\baddr,\eaddr,\aaddr)$ and $\perm' \sqsubseteq\perm$,
        $k = 1$
      \item \label{case:ftlr:move-cca-etc:cca-seal}(cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$,
        $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $\Phi_S(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$ and $\Phi_T(r_1) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $k = 1$
      \item \label{case:ftlr:move-cca-etc:move}(move) $w_1 = \Phi_S(r_2)$, $w_1' = \Phi_T(r_2)$, and $\isLinear{w_1} \Rightarrow w_2 = w_2' = 0$, and $\neg \isLinear{w_1} \Rightarrow (w_2 = \Phi_S(r_2) \wedge w_2' = \Phi_T(r_2)$) and $r_1 \neq r_2$ and $k = 2$.
      \item \label{case:ftlr:move-cca-etc:move-eq}(move) $w_1 = \Phi_S(r_1)$, $w_1' = \Phi_T(r_1)$ and $k = 1$.
      \item \label{case:ftlr:move-cca-etc:cseal}(cseal) $w_1 = \sealed{\sigma,\Phi_S(r_1)}$, $w_1' = \sealed{\sigma,\Phi_T(r_1)}$, $\Phi_S(r_2) = \Phi_T(r_2) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \le \sigma \le \sigma_\eaddr$, and $k=1$, and either $\Phi_S$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ or $\ta \# [\baddr,\eaddr]$.
      \item \label{case:ftlr:move-cca-etc:split-normal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$, $s < \eaddr$,
        $w_1 = w_1' = ((\perm,\lin),\baddr,n,\aaddr)$, $w_2 = w_2' =
        ((\perm,\lin),n+1,\eaddr,\aaddr)$, $w_3 = w_3' = \linCons{\Phi_S(r_3)}$, $k=3$.
      \item \label{case:ftlr:move-cca-etc:split-seal} (split) $\Phi_T(r_3) = \Phi_S(r_3) =
        \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, $\sigma_\baddr \leq s$, $s <
        \sigma_\eaddr$, $w_1 = w_1' = \seal{\sigma_\baddr,s,\sigma}$, $w_2 =
        w_2' = \seal{s+1,\sigma_\eaddr,\sigma}$, $k=2$.
      \item \label{case:ftlr:move-cca-etc:split-stack} (split) $\Phi_S(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$,
        $\Phi_T(r_3) = ((\perm,\linear),\baddr,\eaddr,\aaddr)$, $\baddr \leq s$,
        $s < \eaddr$, $w_1 = \stkptr{\perm,\baddr,n,\aaddr}$, $w_1' =
        ((\perm,\linear),\baddr,s,\aaddr)$, $w_2 =
        \stkptr{\perm,s+1,\eaddr,\aaddr}$,

@@

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.
    (I have done this, and it does not seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump. If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.} and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.} as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\normal),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrvg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
  From assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, the
  result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
  \dominique{No: we need to use Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} together with the reasonability of registers at a boundary crossing (if there is one).}

  This leaves the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know
    \[
      \npair[n]{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrvg{\trust}(W_{R,\stk})
    \]
    which by the $\mathit{stackReadCondition}$ gives $S \subseteq \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n]{[\baddr_\stk,\eaddr_\stk]} \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

    Pick $R_R' = R_R$.
    For $r \neq r_1,r_2$, we have
    \[
      \npair[n-1]{(\Phi_S(r),\Phi_T(r))} \in \lrv(R_R(r))
    \]
    by assumption and Lemma~\ref{lem:downwards-closed}.

    For $r_1$ use Lemma~\ref{lem:lrv-relates-linearity} and consider the following 2 cases:
    \begin{itemize}
    \item $\ta \# [\baddr,\eaddr]$: by assumption this entails $\trust = \untrusted$.

      By assumption we have $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\untrusted}(R_R(r_2))$ which gives us the following facts:
      \begin{itemize}
      \item $[\sigma_\baddr,\sigma_\eaddr] \# (\gsigrets \uplus \gsigcloss)$
      \item $\forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp \exists r \in \pwheap[R_R(r_2)] \ldotp \pwheap[R_R(r_2)](r) = (\pure,\_,H_\sigma) \wedge H_\sigma \; \sigma' \nequal (\lrvg{\untrusted} \circ \xi)$
      \end{itemize}

      This means that for $\sigma$ there is a region $r$ for which $\pwheap[R_R(r_2)](r) = (\pure,\_,H_\sigma)$ and $H_\sigma \; \sigma' \nequal (\lrvg{\untrusted} \circ \xi)$.
      Pick this as the region in the sealed case and $\sigrets' = \emptyset$,
      $\sigcloss = [\sigma_\baddr,\sigma_\eaddr]$, and $\mscode = [\baddr,\eaddr] \mapsto 0$.
      We now need to show the following:
      \begin{itemize}
      \item $H_\sigma \; \sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma$

        To this end let $\hat{W}$ be given and show
        \[
          H_\sigma \; \sigma \; \hat{W} \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma \; \hat{W}
        \]
        By transitivity of $n$-equality it suffices to show $H_\sigma \; \sigma' \; \hat{W} \nequal \lrvg{\untrusted} \circ \xi(\hat{W})$, which follows by assumption and $H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma \; \hat{W} \nequal \lrvg{\untrusted} \circ \xi(\hat{W})$ which follows by definition of $H^\mathrm{code,\square}_\sigma$ and the fact that $\sigma \in \sigcloss$ and $\ta \# [\baddr,\eaddr]$.

      \item $\npair[n']{(\Phi_S(r_1),\Phi_T(r_1))} \in H_\sigma \; \sigma \; \xi^{-1}(R_R(r_1)) \text{ for all $n' < n$}$

        which corresponds to showing $\npair[n']{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\untrusted}(R_R(r_1))$ which is true by assumption and Lemma~\ref{lem:downwards-closed}.
      \item $(\isLinear{\vsc_S} \Rightarrow \forall W' \future R_R(r_1), W_o, n' < n-1, \npair[n']{(\vsc_S',\vsc'_T)} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \npair[n']{\vsc_S,\vsc_S',\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o))$

        Let $W' \future R_R(r_1)$, $W_o$, $n' < n$, $\npair[n']{(\vsc_S',\vsc'_T)} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(W_o)$.
        Further let $n'' \le n'$ be given and assume $\npair[n'']{(\reg_S,\reg_T)} \in \lrrg{\untrusted}(\{\rdata\})(W_R)$, $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.

        Now consider the following cases:
        \begin{itemize}
        \item $\exec{\vsc_S'}$:

          In this case, pick $\Phi_S' = \Phi_T' = \failed$ (as xjump fails).
          It is trivial to show $\npair{\Phi_S',\Phi_T'} \in \lro$.
        \item $\nonExec{\vsc_S'}$:

          In this case consider what $\Phi_S(r_1)$ is:\\
          If $\Phi_S(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm \in \{\rwx, \rx\}$:

          If $\perm = \rwx$, then we have a contradiction with $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\untrusted}(R_R(r_1))$.

          If $\perm = \rx$, then by Lemma~\ref{lem:safe-cap-exec-is-normal} we have a contradiction with $\isLinear{\Phi_S(r_1)}$.
          \\
          \\
          Otherwise (not $\Phi_S(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm \in \{\rwx, \rx\}$):\\

          In this case, pick $\Phi_S' = (\ms_S,\reg_S\update{\pcreg}{\Phi_S(r_1)}\update{\rdata}{\vsc_S'},\stk,\ms_\stk)$ and $\Phi_T' = (\ms_T,\reg_T\update{\pcreg}{\Phi_T(r_1)}\update{\rdata}{\vsc_T'})$.
          In this case, the next step of execution fails which makes it trivial
          to show $\npair{\Phi_S',\Phi_T'} \in \lro$.
        \end{itemize}
      \item $(\nonLinear{\src{\vsc_S}} \Rightarrow \forall W' \future \purePart{R_R(r_2)}, W_o, n' < n-1, \npair[n']{(\vsc_S',\vsc'_T)} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \npair[n']{\vsc_S,\vsc_S',\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o))$

        Let $W' \future \purePart{R_R(r_1)}$, $W_o$, $n' < n$, $\npair[n']{(\vsc_S',\vsc'_T)} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(W_o)$.
        Further let $n'' \le n'$ be given and assume $\npair[n'']{(\reg_S,\reg_T)} \in \lrrg{\untrusted}(\{\rdata\})(W_R)$, $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.

        Now consider the following cases:
        \begin{itemize}
        \item $\exec{\vsc_S'}$:

          In this case, pick $\Phi_S' = \Phi_T' = \failed$ (as xjump fails).
          It is trivial to show $\npair{\Phi_S',\Phi_T'} \in \lro$.
        \item $\nonExec{\vsc_S'}$:

          In this case consider what $\Phi_S(r_1)$ is.\\
          If $\Phi_S(r_1) = ((\perm',\lin'),\baddr',\eaddr',\aaddr')$ and $\perm' \in \{\rwx, \rx\}$:

          If $\perm' = \rwx$, then we have a contradiction with $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\untrusted}(R_R(r_1))$.

          If $\perm' = \rx$, then the result follows from \ref{lem:untrusted-sealed-capability}.
        \end{itemize}
      \end{itemize}
    \item $\ta \subseteq [\baddr,\eaddr]$: by assumption this entails $\trust = \trusted$.

      Further, we know $\Phi_S$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$, so by the reasonability assumption on $\Phi_S$, we know $\sigma \in \gsigcloss$ and one of the following holds:
      \begin{itemize}
      \item $\exec{\Phi(r_1)}$ and $\Phi(r_1)$ behaves reasonably up to $n - 1$ steps.
      \item $\nonExec{\Phi(r_1)}$ and $\Phi(r_1)$ is reasonable up to $n - 1$ steps in memory $\Phi.\ms$ and free stack $\Phi.\ms_\stk$
      \end{itemize}
      By $\sigma \in \gsigcloss$ we can conclude that $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \not\in \lrvg{\untrusted}(W)$ which means that the assumption $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trusted}(W)$ gives us $r \in \dom(\pwheap)$ such that $\pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\mscode,\gc}$, $[\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)$ and $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$, $\dom(\mscode) \subseteq \ta$.

      Now pick $r$ and show
      \begin{itemize}
      \item $\npair[n']{(\Phi_S(r_1),\Phi_T(r_1))} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(R_R(r_1)) \text{ for all $n' < n-1$}$

        This amounts to showing (1) assuming $\exec{\Phi_S(r_1)}$ show $\npair[n']{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\trusted}(R_R(r_1))$, which is true by assumption and Lemma~\ref{lem:downwards-closed}.

        (2) Assuming $\nonExec{\Phi_S(r_1)}$ show $\npair[n']{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\untrusted}(R_R(r_1))$, which follows by assumption, Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} and Lemma~\ref{lem:downwards-closed}.
      \item
        \[
          \begin{array}{l}
            (\isLinear{\Phi_S(r_1)} \Rightarrow \\
            \quad\forall W' \future R_R(r_1), W_o, n' < n, \npair[n']{(\vsc_S',\vsc'_T)} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
            \qquad \npair[n']{\Phi_S(r_1),\vsc_S',\Phi_T(r_1),\vsc_T'} \in \lrexj(W'\oplus W_o))
          \end{array}
        \]

        Let $W' \future R_R(r_1)$, $W_o$, $n' < n$, $\npair[n']{(\vsc_S',\vsc'_T)} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(W_o)$.
        Further let $n'' \le n'$ be given and assume $\npair[n'']{(\reg_S,\reg_T)} \in \lrrg{\untrusted}(\{\rdata\})(W_R)$, $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.

        Now consider the following cases:
        \begin{itemize}
        \item $\exec{\vsc_S'}$:

          In this case, pick $\Phi_S' = \Phi_T' = \failed$ (as xjump fails).
          It is trivial to show $\npair{\Phi_S',\Phi_T'} \in \lro$.
        \item $\nonExec{\vsc_S'}$:

          In this case consider what $\Phi_S(r_1)$ is:\\
          If $\Phi_S(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm \in \{\rwx, \rx\}$:

          If $\perm = \rwx$, then we have a contradiction with $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\trusted}(R_R(r_1))$.

          If $\perm = \rx$, then by Lemma~\ref{lem:safe-cap-exec-is-normal} we have a contradiction with $\isLinear{\Phi_S(r_1)}$.
          \\
          \\
          Otherwise (not $\Phi_S(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$ and $\perm \in \{\rwx, \rx\}$):\\

          In this case, pick $\Phi_S' = (\ms_S,\reg_S\update{\pcreg}{\Phi_S(r_1)}\update{\rdata}{\vsc_S'},\stk,\ms_\stk)$ and $\Phi_T' = (\ms_T,\reg_T\update{\pcreg}{\Phi_T(r_1)}\update{\rdata}{\vsc_T'})$.
          In this case, the next step of execution fails which makes it trivial to show $\npair{\Phi_S',\Phi_T'} \in \lro$.
        \end{itemize}
      \item
        \[
          \begin{array}{l}
            (\nonLinear{\Phi_S(r_1)} \Rightarrow \\
            \quad \forall W' \future \purePart{R_R(r_1)}, W_o, n' < n, \npair[n']{(\vsc_S',\vsc'_T)} \in \codereg{\sigrets,\sigcloss,\mscode,\gc}.H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \\
            \qquad \npair[n']{\Phi_S(r_1),\vsc_S',\Phi_T(r_1),\vsc_T'} \in \lrexj(W'\oplus W_o))
          \end{array}
        \]
